Jeff Goldsmith

### 2017-08-08 papers.Rmd
fixing incorrect link for paper
updated papers list — citation for sofr review paper

@@

P. T. Reiss, **J. Goldsmith**, H. L. Shang, R. T. Ogden.
Methods for Scalar-on-Function Regression (2017+).
<i> International Statistical Review, </i>
accepted.

**J. Goldsmith**, J. E. Schwartz.
Variable Selection in the Functional Linear Concurrent Model (2017+).
<i> Statistics in Medicine, </i>
accepted.
[[PDF](Downloads/VBVS.pdf)
| [GitHub](https://github.com/jeff-goldsmith/vbvs.concurrent)]

J. Gertheiss, **J. Goldsmith**, H. L. Shang, A.-M. Staicu (2017).
A note on modeling sparse exponential-family functional response curves.
<i> Computational Statistics and Data Analysis, </i>
<b>105</b> 46-52.
[[Link](http://www.sciencedirect.com/science/article/pii/S0167947316301748) |
[GitHub](https://github.com/jeff-goldsmith/vbvs.concurrent)]

@@

A. Castano, M. Haq, D. Narotsky, **J. Goldsmith**, R. L. Weinberg, R. Morgenstern, T. Pozniakoff, F. L. Ruberg, E. J. Miller, J. L. Berk, A. Dispenzieri, M. Grogan, G.
Multicenter Experience of Planar Technetium Pyrophosphate Cardiac Imaging: Does Preferential Cardiac Uptake Predict Survival in Patients with ATTR Cardiac Amyloidosis?
<i> JAMA Cardiology, </i>
<b>1</b> 880-889.

@@

H. Sorensen, **J. Goldsmith**, L. Sangalli. (2013).
An Introduction with Medical Applications to Functional Data Analysis.
<i> Statistics in Medicine. </i>
<b>32</b> 5222-5240.
[[Link](http://www.tandfonline.com/doi/abs/10.1080/10618600.2012.679241) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/23794794)]

>>>>

A. L. Wong, **J. Goldsmith**, A. D. Forrence, A. M. Haith, and J. W. Krakauer (2017+).
Habitual selection of reaction times.
<i> eLife, </i> 
accepted.

K. M. Diaz, D. J. Krupka, M. J. Chang, I. M. Kronish, N. Moise, **J. Goldsmith**, and J. E. Schwartz (2017+).
	Wrist-based cut-points for moderate- and vigorous-intensity physical activity for the Actical accelerometer in adults.
<i> Journal of Sports Sciences, </i>
accepted.

@@

**J. Goldsmith** and J. E. Schwartz.
Variable Selection in the Functional Linear Concurrent Model (2017+).
<i> Statistics in Medicine, </i>
accepted.
[[PDF](Downloads/VBVS.pdf)
| [GitHub](https://github.com/jeff-goldsmith/vbvs.concurrent)]

P. T. Reiss, **J. Goldsmith**, H. L. Shang, and R. T. Ogden.
Methods for Scalar-on-Function Regression (2017+).
<i> International Statistical Review, </i>
<b>85</b> 228-249.

J. Gertheiss, **J. Goldsmith**, and A.-M. Staicu (2017).
A note on modeling sparse exponential-family functional response curves.
<i> Computational Statistics and Data Analysis, </i>
<b>105</b> 46-52.
[[Link](http://www.sciencedirect.com/science/article/pii/S0167947316301748) |
[GitHub](https://github.com/jeff-goldsmith/vbvs.concurrent)]

@@

A. Castano, M. Haq, D. Narotsky, **J. Goldsmith**, R. L. Weinberg, R. Morgenstern, T. Pozniakoff, F. L. Ruberg, E. J. Miller, J. L. Berk, A. Dispenzieri, M. Grogan, G. Johnson, S. Bokhari, and M. S. Maurer (2016).
Multicenter Experience of Planar Technetium Pyrophosphate Cardiac Imaging: Does Preferential Cardiac Uptake Predict Survival in Patients with ATTR Cardiac Amyloidosis?
<i> JAMA Cardiology, </i>
<b>1</b> 880-889.

@@

H. Sorensen, **J. Goldsmith**, L. Sangalli. (2013).
An Introduction with Medical Applications to Functional Data Analysis.
<i> Statistics in Medicine. </i>
<b>32</b> 5222-5240.
[[Link](http://onlinelibrary.wiley.com/doi/10.1002/sim.5989/abstract) |
[PubMed](https://www.ncbi.nlm.nih.gov/pubmed/24114808)]
